*Supplementary Material 1*

### 2022-06-21 ms/manuscript.Rmd
Add histogram of sequence lengths

The "plants" division of GenBank release 249 (cutoff date 2022-04-15) was downloaded from the NCBI FTP server and a local database including only ferns and outgroups (selected seed plants, lycophytes, bryophytes, and algae) created using the restez R package [@Bennett2018a].
GenBank accession numbers corresponding to sequences potentially matching each locus were obtained by querying the GenBank with terms including the locus name (`r eg`, "rbcL"), "Polypodiopsida[ORGN]", and a date cuteoff matching the current GenBank release.
Names including the terms "aff." or "cf.", hybrid formulas, and environmental DNA samples were excluded.
Sequences were then pulled from the local database in FASTA format by GenBank accession number.
There is no formal definition of genomic vs. Sanger sequences in GenBank, so we used an empirical sequence length cutoff to distinguish between Sanger (≤ `r number(7000)` bp) and plastome (> `r number(7000)` bp) accessions with the "[SLEN]" term.

>>>>

The "plants" division of GenBank release 249 (cutoff date 2022-04-15) was downloaded from the NCBI FTP server and a local database including only ferns and outgroups (selected seed plants, lycophytes, bryophytes, and algae) created using the restez R package [@Bennett2018a].
GenBank accession numbers corresponding to sequences potentially matching each locus were obtained by querying the GenBank with terms including the locus name (`r eg`, "rbcL"), "Polypodiopsida[ORGN]", and a date cuteoff matching the current GenBank release.
Names including the terms "aff." or "cf.", hybrid formulas, and environmental DNA samples were excluded.
Sequences were then pulled from the local database in FASTA format by GenBank accession number.
There is no formal definition of genomic vs. Sanger sequences in GenBank, so we used an empirical sequence length cutoff to distinguish between Sanger (≤ `r number(7000)` bp) and plastome (> `r number(7000)` bp) accessions with the "[SLEN]" term (**`r s_figure("seqlen")`**.).

### 2022-06-21 ms/si.Rmd
Add histogram of sequence lengths

>>>>

```{r seqlen, fig.width = 7, fig.height = 4, eval = params$doc_type != "manual"}
fern_slen_tib <- read_from_cache(
  "fern_slen_tib", here::here("_supp_store")) %>%
  # Add column for plastome or not
  mutate(
    plastome = if_else(
      str_detect(def, "complete genome"),
      "A. 'complete genome'",
      "B. other"
    ),
    plastome = factor(plastome, levels = c("A. 'complete genome'", "B. other"))
  )

ggplot(fern_slen_tib, aes(slen)) +
  geom_vline(xintercept = 7000, color = "red") +
  geom_histogram(bins = 100) +
  scale_x_log10() +
  scale_y_continuous(expand = expansion(mult = c(0, .05))) +
  labs(x = "Sequence length (bp)", y = "Count (num. accessions)") +
  facet_wrap(vars(plastome))
```

**`r s_figure("seqlen")`**.
Histogram of sequence lengths (bp; log-scale) of fern accessions in GenBank release v249.
Fern accessions obtained by querying GenBank for “Polypodiopsida[ORGN]” with length 10--200,000 bp.
**A.** Sequences with the term 'complete genome' in their description (`r eg`, "Angiopteris evecta chloroplast, complete genome").
**B.** Other sequences (those without 'complete genome' in their description).
Vertical red line at 7,000 bp indicates empirical length cutoff used to differentiate between between Sanger (≤ 7,000 bp) and plastome (> 7,000 bp) accessions.
Note that "other" includes some whole plastome accessions that cannot be distinguished based on description alone (e.g., "UNVERIFIED: Nephrolepis biserrata plastid sequence"); these are mostly above 7,000 bp.
